\documentclass{beamer}

\usepackage{beamerthemesplit}

\title{A Neural Network model to analyze how intervention of BMI would affect incidence of diabetes }
\author{Thomas Richardson\\
 Yuan Zhang}
\date{\today}

\begin{document}

\frame{\titlepage}

\section[Outline]{}
\frame{\tableofcontents}

\section{Introduction}
\subsection{Overview of SAS Project}
\frame
{
  \frametitle{Overview of SAS Project}

  \begin{itemize}
  \item {Rising Health Care costs in US prompts need for change in Health Care Policy}
  \item {Assess healthcare costs associated with diabetes.}
  \item {Determine how to reduce diabetes incidence as a means of reducing healthcare costs.}
  \item {Enact measures to reduce risk of diabetes in at-risk population}
  \item{Proposed measure:  reduce BMI by 10\%  in target population. }
  \item{Data Set:  43 parameters for 50,000+ individuals.}
  \end{itemize}
}
\subsection{Diabetes Background}
\frame
{
  \frametitle{Overview of Diabetes}

  \begin{itemize}
  \item {}
  \item {}
  \item {}
  \end{itemize}
 
}
\section{Proposed Plan}
\subsection{Overview of Plan}
\frame
{
\frametitle{Plan Summary}

  \begin{itemize}
  \item {Select set of most relevant parameters to use in analysis.}
  \item {Train and validate neural network with selected parameters.}
  \item {Observe how introducing the proposed measure affects the predicted incidence of diabetes.}
  \end{itemize}
}

\frame
{
 \frametitle{Parameter Reduction}

  \begin{itemize}
  \item {Remove parameters that are likely caused or highly influenced by having diabetes (use literature to do this).}
  \item {Use correlation / covariance measures to weed out less influential parameters.}
  	\begin{itemize}
 	 \item {We used Partial Least Squares for this task.}
	\end{itemize}
 % \item {PLS is an extension of multiple linear regression, and creates a linear model using eigenvectors for the matrix resulting from the product of the factors matrix (subset of parameters from above) and the response matrix (incidence of diabetes).}
  \item{May also want to use other measures to determine relevance of parameters.}
  \end{itemize}
}

%Model Inputs
\subsection{Neural Network Output}
\frame
{
\frametitle{Interpreting Output}
  \begin{itemize}
  \item {Can cluster output data in order to determine an "at-risk" population.}
  \item {Can modify input BMI to predict reduction in diabetes incidence due to proposed measure.}
  \item {Future work will include determining healthcare costs resulting from diabetes.}
  \end{itemize}
}

% Surveillance Stategies

\subsection{Surveillance Strategies}
\frame
{
\frametitle{International Guidelines }
  \begin{itemize}
  \item {American Urological Association(AUA)suggests periodic follow-up cystoscopy for bladder cancer patients. However, no specific interval nor duration of follow-ip cystoscopy has been defined}
  \item {European Association of Urology(EAU) has specific follow-up guidelines for low rik, high risk, intermediate risk patients respectively. }
  \item {First International Consultation on Bladder Tumours(FICBT) has specific follow-up recommendations for low risk, high-grade Ta, and CIS patients respectively.}
  \item {National Comprehensive Cancer Network(NCCN) has two specific guidelines for low risk patients and intermediate or high risk patients respectively}
  \item {The recommended follow-up cystoscopy schedules proposed by AUA, EAU, FICBT, and NCCN vary, and debates still exist.}
  \end{itemize}
}

%new subsection of Utilities and Disutilities
%\subsection{Utilities and Disutilities of Test and Treatments}
%\frame
%{
%}


%\section{Other Inputs of The Model}
%\frame{
%\frametitle{Utilities and Disutilities}
%\begin{itemize}
%\item {Assign qualify-of-life weights to each defined state between 0(death) and 1(perfect health)}
%\item {Estimate disutitity of Cystoscopy}
%\item {Estimate disutilities of various treatments for bladder cancers}

%\end{itemize}

%}

\section{Research Questions}
\frame
{
  \frametitle{Specific Research Questions   }

  \begin{itemize}

  \item<1-> {What's the best surveillance strategy with respect to cystoscopy frequency for various risk groups?}
  \item<2-> {Is age a significant factor for the optimal surveillance strategy?}
  \end{itemize}
 
}
\section{Results}
\frame
{
  \frametitle{Methods }

  \begin{itemize}

  \item {simulation}
  \item {sampling of a Markov chain}
  \end{itemize}
 
}
\frame
{
  \frametitle{Preliminary Results }

  
 
}

% Future Work
\section{Future Work}
\frame
{
  \frametitle{Future Work }
  \begin{itemize}

\item<1-> {Combining other non-invasive test methods(biomarkers, cytology ) with cystoscopy, can we design a better surveillance strategy?} 


\end{itemize}

 
}

\end{document}
    